---
title: "Template document"
author: "Robin Linacre"
date: "13/07/2019"
output:
  govdown::govdown_document:
    font: "new-transport" # (default) or "sans-serif"
    favicon: none # or "none" (default) or "govuk" see ?govdown_document
    logo: false # or false (default)
    logo_url: "https://ukgovdatascience.github.io/govdown"
    logo_text: "logo_text"
    page_title: "page_title"
    title: "title"
    phase: beta
    feedback_url: "https://github.com/ukgovdatascience/govdown/issues"
runtime: shiny
---

```{r setup, include=FALSE}

library(govdown)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache=FALSE)
library(shiny)
library(vegawidget)
library(rmarkdown)

```

## R Markdown

This is a template for an R Markdown document which renders to a html website using gov.uk styling.

It re-renders the R Markdown document each time you access the page.  This means that if you read data from s3, when the data updates, the markdown report will update.  To see it in action, you can the data in s3 file by running [this script](update_data.R), and then refresh the deployed app.

We use the [`govdown`](https://github.com/ukgovdatascience/govdown) package for the styling, which means that our pages use the official [gov.uk design system](https://design-system.service.gov.uk/).

I recommend the use of vega lite for html based charts.  You can read more about why [here](https://medium.com/@robin.linacre/why-im-backing-vega-lite-as-our-default-tool-for-data-visualisation-51c20970df39).


```{r echo=FALSE, cache=FALSE}
# Some of these aren't actually required by the report, but without them packrat doesn't realise they're required

data <- s3tools::s3_path_to_full_df("alpha-app-rmarkdown-vegawidget-template/random_data.csv")

# Storing charts as json is recommended as it provides good separation of concerns.
# It also means that the charts can more easily be used in other contexts (other web pages, Python etc.)
my_chart <- vegawidget::as_vegaspec("charts/random_data.json")
my_chart$data <- list("values"=data)
my_chart

```



The mean of the values in the dataframe is `r mean(data$value)`



```{r cars}
# You can also build a vega lite spec in R code as follows.
 spec <- list(
      `$schema` = vegawidget::vega_schema(), # specifies Vega-Lite
      description = "An mtcars example.",
      data = list(values = mtcars),
      mark = "point",
      encoding = list(
        x = list(field = "wt", type = "quantitative"),
        y = list(field = "mpg", type = "quantitative"),
        color = list(field = "cyl", type = "nominal")
      )
    )
  vg_spec <-vegawidget::as_vegaspec(spec)
  vegawidget::vegawidget(vg_spec)

```
