---
title: "Template document"
author: "Robin Linacre"
date: "13/07/2019"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache=FALSE)
library(shiny)
library(vegawidget)
```

## R Markdown

Here is an R Markdown document which includes vega lite charts.

It re-renders the R Markdown document each time you access the page.  This means that if you read data from s3, when the data updates, the markdown report will update.

There is a file called data.csv that is stored in s3://alpha-app-rmarkdown-vegawidget-template/data.csv.  

We're going to generate a report from this file.

You can change the data in this file by running [this script](update_data.R)


```{r echo=FALSE, cache=FALSE}

# data <- read.csv("data/random_data.csv")

dice_roll <- sample(1:6, size=50, replace=TRUE)
person <- sample(c("Robin", "John", "David", "Jane", "Chloe", "Lily", "Sam"), size=50, replace=TRUE)
value <- runif(100,0,100)
data <- data.frame(person =person, dice_roll = dice_roll, value=value)


my_chart <- vegawidget::as_vegaspec("charts/random_data.json")
my_chart$data <- list("values"=data)
my_chart

```



The mean of the values in the dataframe is `r mean(data$value)`

```

```{r cars}
 spec <- list(
      `$schema` = vegawidget::vega_schema(), # specifies Vega-Lite
      description = "An mtcars example.",
      data = list(values = mtcars),
      mark = "point",
      encoding = list(
        x = list(field = "wt", type = "quantitative"),
        y = list(field = "mpg", type = "quantitative"),
        color = list(field = "cyl", type = "nominal")
      )
    ) 
  vg_spec <-vegawidget::as_vegaspec(spec)
  vegawidget::vegawidget(vg_spec)
  
```

```{r echo=FALSE}

data <- read.csv("data/seattle.csv")
seattle <- vegawidget::as_vegaspec("charts/seattle.json")
seattle$data <- list("values"=data)
seattle


```

